A finite-state morphological transducer for Kyrgyz

### 2011-10-14 dev/paper/paper.tex
Mirlan's affiliation

\author {Jonathan North Washington, \\
Indiana University,\\
Bloomington, IN 47405-7000 (USA)\\
\texttt{jonwashi@indiana.edu} \and 
Mirlan Ipasov,\\
xxx\\
yyy (Kyrgyzstan)\\
\texttt{mipasov@gmail.com} \and
Francis M. Tyers\\
Dept.\ Lleng.\ i Sist. Informàtics \\  
Universitat d'Alacant\\
E-03071 Alacant (Spain)\\
\texttt{ftyers@dlsi.ua.es} 
 }

>>>>

\author {Jonathan North Washington, \\
Departments of Linguistics and Central Eurasian Studies,\\
Indiana University,\\
Bloomington, IN 47405-7000 (USA)\\
\texttt{jonwashi@indiana.edu} \and 
Mirlan Ipasov,\\
Computer Engineering and Mathematics Department\\
International Ataturk Alatoo University\\
Bishkek (Kyrgyzstan)\\
\texttt{mipasov@gmail.com} \and
Francis M. Tyers\\
Dept.\ Lleng.\ i Sist. Informàtics \\  
Universitat d'Alacant\\
E-03071 Alacant (Spain)\\
\texttt{ftyers@dlsi.ua.es} 
 }
